Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-22 writeup/rocha_etal.tex
Minor edits

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig4.pdf}
 \caption{\small LLC4320 wavenumber-frequency spectrum of SSH variance in (a) April and (b) October.
          (c) Wavenumber spectrum of SSH variance --- the integral of (a) and (b) over frequency.
          In (a) and (b), the light gray shaded region depicts the dispersion relations for inertia-gravity
          waves from mode 1 through mode 4 across the latitudinal domain; horizontal dashed lines represent the semi-diurnal
          lunar tidal frequency ($M_2$), and the inertial frequency at mid-latitude
          ($f_{32.5}$) and its first harmonic (2$f_{32.5}$). }
  \label{fig4}
 \end{center}
\end{figure*}

@@

In the context of SWOT, our results suggest that if one is interested
only in the geostrophic flow, so that surface velocity can be diagnosed
from SSH, then the noise-to-signal ratio will have a strong seasonality owing
to the presence of incoherent IGWs --- the coherent fraction of internal tides may be removed
efficiently.
An important caveat is that the Kuroshio Extension may be typical of a mesoscale-rich
subtropical regions, but it is unlikely to be
representative of other regions such as low-eddy-kinetic-energy eastern boundary
currents.  We plan to report on the geographic variability of submesoscale
seasonality in a future study.

>>>>

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.8\textwidth]{figs/fig4.pdf}
 \caption{\small LLC4320 wavenumber-frequency spectrum of SSH variance in (a) April and (b) October.
          (c) Wavenumber spectrum of SSH variance --- the integral of (a) and (b) over frequency.
          In (a) and (b), the light gray shaded region depicts the dispersion relations for inertia-gravity
          waves from mode 1 through mode 4 across the latitudinal domain; horizontal dashed lines represent the semi-diurnal
          lunar tidal frequency ($M_2$), and the inertial frequency at mid-latitude
          ($f_{32.5}$) and its first harmonic (2$f_{32.5}$). }
  \label{fig4}
 \end{center}
\end{figure*}

@@

In the context of SWOT, our results suggest that if one is interested
only in the geostrophic flow, so that surface velocity can be diagnosed
from SSH, then the noise-to-signal ratio will have a strong seasonality owing
to the presence of IGWs --- the coherent fraction of internal tides may be removed
efficiently.
An important caveat is that the Kuroshio Extension may be typical of a mesoscale-rich
subtropical regions, but it is unlikely to be
representative of other regions such as low-eddy-kinetic-energy eastern boundary
currents.  We plan to report on the geographic variability of submesoscale
seasonality in a future study.

### 2016-08-22 writeup/rocha_etal_supporting-info.tex
Removes annoying of course
Minor edits

 \begin{figure}
    \begin{center}
      \setfigurenum{S4}
      \includegraphics[width=40pc]{figs/figS4.pdf}
   \caption{Potential density: a comparison between Roemmich-Gilson Argo
           climatology [updates from \cite{roemmich_gilson2009}] (a, b) and the 1/24$^\circ$ (c, d)
           and  1/48$^\circ$ (e, f) LLC simulations. Of course, the Argo climatology is smoother,
           owing to lower resolution and long-term averaging. Nonetheless, simulations reproduce the strong
           seasonality in the stratification. The upper ocean is weakly stratified in late winter/early fall
           and re-stratifies in summer. Argo climatology and LLC simulations mixed-layer depths are consistent
            during all seasons (not shown). The Argo climatology is available online at
           \texttt{http://sio-argo.ucsd.edu/RG\_Climatology.html}.}
   \label{figS2_1}
   \end{center}
 \end{figure}

@@

 \begin{figure}
    \begin{center}
      \setfigurenum{S7}
      \includegraphics[width=40pc]{figs/figS7.pdf}
   \caption{LLC4320 Wavenumber-frequency spectrum of KE in (a) April
    and (b) October. (c) Wavenumber spectrum of SSH variance — the integral of (a)
    and (b) over frequency. In (a) and (b), the light gray shaded region depicts the
    dispersion relations for inertia-gravity waves from mode 1 through mode 4 across
    the latitudinal domain; horizontal dashed lines represent the semi-diurnal lunar
    tidal frequency (M2), and the inertial frequency at mid-latitude (f32.5) and its
    first harmonic (2f32.5).}
   \label{figS7}
   \end{center}
 \end{figure}

>>>>

 \begin{figure}
    \begin{center}
      \setfigurenum{S4}
      \includegraphics[width=40pc]{figs/figS4.pdf}
   \caption{Potential density: a comparison between Roemmich-Gilson Argo
           climatology [updates from \cite{roemmich_gilson2009}] (a, b) and the 1/24$^\circ$ (c, d)
           and  1/48$^\circ$ (e, f) LLC simulations. The Argo climatology is smoother
           owing to lower resolution and long-term averaging. Nonetheless, simulations reproduce the strong
           seasonality in the stratification. The upper ocean is weakly stratified in late winter/early fall
           and re-stratifies in summer. Argo climatology and LLC simulations mixed-layer depths are consistent
            during all seasons (not shown). The Argo climatology is available online at
           \texttt{http://sio-argo.ucsd.edu/RG\_Climatology.html}.}
   \label{figS2_1}
   \end{center}
 \end{figure}

@@

 \begin{figure}
    \begin{center}
      \setfigurenum{S7}
      \includegraphics[width=40pc]{figs/figS7.pdf}
   \caption{LLC4320 Wavenumber-frequency spectrum of KE in (a) April
    and (b) October. (c) Wavenumber spectrum of SSH variance — the integral of (a)
    and (b) over frequency. In (a) and (b), the light gray shaded region depicts the
    dispersion relations for inertia-gravity waves from mode 1 through mode 4 across
    the latitudinal domain; horizontal dashed lines represent the semi-diurnal lunar
    tidal frequency (M2), and the inertial frequency at mid-latitude ($f_{32.5}$) and its
    first harmonic ($2f_{32.5}$).}
   \label{figS7}
   \end{center}
 \end{figure}
